Sulfur Dioxide at Water's Surface

### 2010-12-29 Background.tex
New section on the so2 transit orientation analysis + pictures

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/molecularframesmall.png}
		\caption{The body-fixed are defined with the molecular plane in the x-z plane, and the z-axis aligned to the molecular bisector. This sets the y-axis normal to the molecular plane, and one of the molecular bonds in the positive x direction.}
		\label{fig:molecular-frame}
	\end{center}
\end{figure}

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/wateranglessmall.png}
		\caption{The visual representation of the angles $\theta$ and $\phi$ used to define molecular orientation of \suldiox~and \wat~relative to the reference axis. $\theta$ is the value of the ``tilt'' of the molecular bisector, and $\phi$ is the ``twist'' that indicates how flat the molecule is relative to the interfacial plane.}
		\label{fig:water-angles}
	\end{center}
\end{figure}

>>>>

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/molecularframesmall.png}
		\caption{The body-fixed axes are defined with the x-z plane formed by the three atoms, and the z-axis aligned to the molecular bisector. This sets the y-axis normal to the molecular plane, and one of the bonds in the positive x direction.}
		\label{fig:molecular-frame}
	\end{center}
\end{figure}

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/wateranglessmall.png}
		\caption{The definition of the angles $\theta$ and $\phi$ used to define molecular orientation of \suldiox~and \wat~relative to a reference axis. $\theta$ is the value of the ``tilt'' of the molecular bisector from the reference axis. $\phi$ is the ``twist'' angle that indicates how flat the molecule is relative to the interfacial plane, and is formed between the vector normal to the molecular plane (the body-fixed y-axis) and the reference axis.}
		\label{fig:water-angles}
	\end{center}
\end{figure}

### 2010-12-29 TransitResults.tex
New section on the so2 transit orientation analysis + pictures

\subsection {Neat-\wat~Single \suldiox System}

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/so2transitangles.png}
		\caption{}
		\label{fig:so2-transit-angles}
	\end{center}
\end{figure}

\subsection {Saturated \wat~System}

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/so2transitsaturatedangles.png}
		\caption{}
		\label{fig:so2-transit-saturated-angles}
	\end{center}
\end{figure}

>>>>

\subsection {\suldiox~Orientation}

	The orientation of a \suldiox~molecule adsorbing to an aqueous surface was determined through an analysis process to find the angles $\theta$ and $\phi$ (figure \ref{fig:water-angles}). For each timestep of the SMD simulations the orientation angles were determined for a single \suldiox~as it was pulled into the water slab, both in the neat-\wat~and saturated slab systems. The resulting values were collected for the 50 simulations for both systems, and the angle values were binned indexed with the position of the \suldiox~relative to the water slab surface location. The resulting 2-dimensional histograms shown in figure \ref{fig:so2-transit-angles} show the orientation trend for the \suldiox~in the gas phase, near the aqueous surface, and after entering the water bulk.

\begin{figure}[h!]
	\begin{center}
		\includegraphics[scale=1.0]{images/so2transitorientationsmall.png}
		\caption{}
		\label{fig:so2-transit-angles}
	\end{center}
\end{figure}

	From its starting position 20\angs above the water surface, until the \suldiox~moves to within 5\angs of the surface of both systems, the orientation is isotropic in both $\theta$ and $\phi$. Upon approaching the saturated surface at approx. 5\angs, the \suldiox~$\phi$ orientation distribution begins to cluster near $\cos(\phi)=1$, with the $\theta$ distribution remaining more isotropic, but with a trend of $\cos(\theta)>0$. At 5\angs the \suldiox~begins interacting with the other \suldiox~molecules that sit atop the water, and the resulting orientation distribution suggests that contact with the \suldiox~layer causes the adsorbing molecule to lie more flat to the surface. Within this same region from 0-5\angs above the surface, the $\phi$ distribution of the neat-\wat~system remains isotropic. The intensity of the distribution (darker blue) also indicates that the \suldiox~spends little time in this region, as it is quickly adsorbed further into the water bulk.

	Just below the water surface as the distance moves into negative values, both systems show clear orientational preferences. In both systems the bisector orientation clusters such that $\cos(\theta)<0.5$, with most of the distribution intensity around $\cos(\theta)=1$. This suggests that \suldiox~in a water surface orients with the sulfur pointing into the water bulk, and the oxygens pointing towards the surface water molecules.

	Differences occurr between the system orientation profiles once the \suldiox~has moved further than 10\angs below the surface. While both $\theta$ and $\phi$ hold the same trend from just under the surface through to the bulk of the slab in the saturated system, the orientation profile becomes much more isotropic past 10\angs under the surface of the neat-\wat~system. The orientation effect is shallower under the neat-\wat~surface. However, the orientation distribution peaks most intensely, and more tightly clustered with the \suldiox~bisector aligning with the surface normal, just underneath the neat-\wat~surface than the saturated one. The distributions thus show an orienting force extending deeper into the surface of the saturated system than the neat-\wat~system. In terms of how deeply the \suldiox~molecule is oriented, the interfacial region of the saturated system is larger and extends further into the aqueous bulk.
